Create final evaluation dataset

### 2022-03-14 data-cleaning/03b-evaluation-dataset.Rmd
add label indicator to eval_ds

```{r}
auto_label %>% 
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique()
```

@@

To remove these, I'll start by expanding these columns to have one column per label. Below, w

```{r}
manu_label <- manu_label %>%
  separate_rows(., label, sep = "; ", convert = FALSE) %>%
  # clean up mismatches
  mutate(label = case_when(
    label == "women's health" ~ "health",
    label == "undue" ~ "undue burden",
    label == "rights" ~ "women's rights",
    label %in% c("reveal", "uncertainty") ~ "evidence",
    T ~ label
  )) %>% 
  # remove instances of (1) and frames we aren't concerned w/rn
  filter(!grepl("1", label),
         !(label %in% c("final authority", "intersectionality", "equal protection", "primary authority"))) %>%
  # collapse cols
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique()
```

>>>>

```{r}
auto_label %>% 
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique() %>% 
  nrow()
```

Add in column indicating that these texts were automatically labeled

```{r}
auto_label <- auto_label %>% mutate(manu_label = 0)
```

@@

To remove these, I'll start by expanding these columns to have one column per label. The inconsistent labels will be corrected and irrelevant information will be removed. At the end, we re-concatenate labels to have one row per case/brief/text. Also add column indicating these texts were manually labeled.

```{r}
manu_label <- manu_label %>%
  separate_rows(., label, sep = "; ", convert = FALSE) %>%
  # clean up mismatches
  mutate(label = case_when(
    label == "women's health" ~ "health",
    label == "undue" ~ "undue burden",
    label == "rights" ~ "women's rights",
    label %in% c("reveal", "uncertainty") ~ "evidence",
    T ~ label
  )) %>% 
  # remove instances of (1) and frames we aren't concerned w/rn
  filter(!grepl("1", label),
         !(label %in% c("final authority", "intersectionality", "equal protection", "primary authority"))) %>%
  # collapse cols
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique() %>% 
  mutate(manu_label = 1)
```
